Downstream analysis: A pipeline to analyse time-course gene expression data

### 2019-02-19 scripts/04_downstream_analysis.Rmd
ENH Pathway enrichment analysis finally works

@@

```{r}
clusters = as.vector(unlist(unique(labels)))
for(cluster in clusters){
    genes = row.names(labels[labels == cluster])
    pathways = KEGGprofile::find_enriched_pathway(
	genes, species="mmu", download_latest=TRUE)
}
```

>>>>

```{r}
gene_names = row.names(labels)
gene_names = gene_names[!is.na(labels)]
labels = labels[!is.na(labels)]
```

@@

```{r}
library(biomaRt)
ensembl = useMart("ensembl")
ensembl = useDataset("mmusculus_gene_ensembl", mart=ensembl)

```

```{r}
clusters = as.vector(unlist(unique(labels)))
for(cluster in clusters){
    print(cluster)
    genes = gene_names[labels == cluster]

    # convert gene names
    genes = getBM(attributes=c("ensembl_gene_id", "entrezgene"),
		       filters="refseq_mrna", values=genes,
		       mart=ensembl)["entrezgene"]
    genes = as.vector(unlist(genes))
    pathways = KEGGprofile::find_enriched_pathway(
	genes, species="mmu",
	download_latest=TRUE)
    print(pathways$stastic)
}
```

### Finding enriched GO terms
